\documentclass[11pt]{article}
\usepackage{common}
\title{CS 287 \\ Assignment 1: Text Classification }
\date{}
\begin{document}

\maketitle{}

In class we covered the basics of text classification, now it is time
to get your hands dirty and implement it.  In this homework assignment
you will replicate current research baseline results for several text
classfication tasks. Before starting the assignment, be sure that you
understand all models described in the slides, in the text, and that
you are familiar with the computational tutorials in HDF5 and Torch.


In this repo are several different data sets containing sentences and 
their classes. Begin by looking through the \texttt{data/} directory 
to get a sense of the different files. The main one we will use is 
called the Stanford Sentiment dataset \citep{socher2013recursive}.


\begin{verbatim}
> head data/stsa.fine.train
4 a stirring , funny and finally transporting re-imagining of 
beauty and the beast and 1930s horror films
1 apparently reassembled from the cutting-room floor of any 
given daytime soap .
1 they presume their audience wo n't sit still for a sociology 
lesson , however entertainingly presented , so they trot out 
the conventional science-fiction elements of bug-eyed monsters 
and futuristic women in skimpy clothes .
2 the entire movie is filled with deja vu moments .
\end{verbatim}

Here the first number gives the correct output class, and the rest of
the line gives the input sentence. There is a similar file for the
validation set. For the test set, we provide only the input. 

As you complete this assignment, we ask that you submit your results
on the test data to the Kaggle competition website at
\url{https://inclass.kaggle.com/c/cs287-hw1} and that you compile your
experiences in a write-up based on the template at
\url{https://github.com/cs287/hw_template}. There are 
several other data sets in the repo that you may find useful for the 
write-up. For the Kaggle competition, you should submit your results 
for just the test set of the SST1 multiclass dataset.
 
\section{Preprocessing}

The first step is to convert the text representations of the data into
features. For this assignment we have provided sample preprocessing
code in \texttt{preprocessing.py}. This code provides preprocessing 
for all the data sets under \texttt{data/}. Please read the code
carefully, as you will be expected to write preprocessing for future
assignments.

The preprocessing code reads in text examples and writes them
out as matrices containing the sparse features for each instance and
the class. Our basic code just outputs unigram features from the data.
The file will output a HDF5 bundle containing the following matrices:
\texttt{train\_input, train\_output, valid\_input, valid\_output,
  test\_input, nfeatures, nclasses}.

\textbf{Note} the structure of \texttt{X\_input} and
\texttt{X\_output}. The input consists of features, where a single row
contains the feature indices $f_1, \ldots, f_k$. However to account
for differing sentence lengths, the row is padded with a special
padding feature 1 to length $k_{max}$ (these must be ignored in your modeling
code).  For this assignment, you should never need to explicitly
construct the sparse vector $\boldx$. The output consists of the
correct class index for each input. We do not provide the correct
output for the test set.

\section{Classification Setup}

The main code for your project should be in \texttt{HW1.lua} and
should be written in Lua/Torch. For this assignment, we ask that you
construct all the models from scratch. You should not use any
(non-debugging) libraries besides the standard Torch framework and HDF5.

\subsection{Prediction and Evaluation}

Be sure you are able to read and output the text data and that you
understand the format. To confirm this, write a function that takes in
the parameters of a linear model, and evaluates it on the validation
set (\texttt{valid\_input} and \texttt{valid\_output}).  The function
should report the results in terms of prediction accuracy. This same
code should be used for each of the linear models described in this
project.

Also be sure you are able output your classification results on the
test data as a text file. Check that you can upload these to the
Kaggle.

\subsection{Hyperparameters}

Several of the models described have explicit hyperparameters that you will 
need to tune. It is your responsibility to cleanly separate these out from 
the models themselves and expose as command-line options. This makes it much 
easier to run experiments and to utilize experimental scripts. 

\subsection{Logging and Reporting}

As part of the write-up, you will need to report on the training and
predictive accuracy of your models. To make this possible, your code
should report on various metrics of the model both at training and
test time. We will leave it up to you on which metrics to log, but we
recommend reporting training speed, training set loss, training set
predictive accuracy, and validation predictive accuracy. It is your
responsibility to convince us that the model is correctly training.

\section{Models}

For this assignment you will implement the three linear models that 
we discussed in class: naive bayes, multiclass logistic regression, 
and multiclass hinge loss.

\subsection{Naive Bayes}

We recommend that you implement multinomial naive Bayes first, since
it is the most efficient and easiest to debug. Follow the description
given in the class notes. Run and report on experiments for tuning the
$\alpha$ hyperparameter.

\subsection{Logistic Regression}

Next implement multiclass logistic regression with L2 regularization
(exposing the $\lambda$ hyperparameter)\footnote{Note that there are several great tutorials for how to implement logistic
regression in Torch online. Do not use these. We expect the
implementation to only utilize the core tensor operations in the
framework. We will get to the some of the higher Torch abstractions in the next assignment.}. For efficiency, training
should be done using minibatch stochastic gradient descent. The size
of the minibatch, the learning rate, and the number of epochs of
training should also be exposed as hyperparameters.


Further notes:

\begin{itemize}
\item It is important to use the log-sum-exp trick discussed in the
  class notes. Without this, you will likely run into numerical
  issues.

\item The Torch \texttt{index} and \texttt{indexAdd} operations should 
  be helpful for improving efficiency.

\item We recommend starting with a subset of the full training data to
  verify that your code is working. You can confirm this by tracking
  the loss of the training set.
\end{itemize}

\subsection{Linear SVM}

Finally implement hinge-loss with L2 regularization (exposing the $\lambda$
hyperparameter). This code should use the same minibatch stochastic
gradient descent code as Logistic Regression. The only difference is
the calculation of the loss and the gradients. 

\subsection{Additional Experiments}

Once these models are constructed, you should also report on
additional experiments on these data sets. We will leave this aspect
open-ended, but suggestion include:

\begin{itemize}
\item Implement 10-fold cross validation and experiment on other included datasets (see \citet{wang2012baselines} or \citet{DBLP:conf/emnlp/Kim14} for lists and results). Or find your own datasets to run online.
\item Include additional features (for instance bigram features, suffix features, cluster features).
\item Experiment with further models (for instance L2 loss SVM \citep{wang2012baselines})
\item Extensive further hyperparameter tuning and experimentation (for instance Spearmint \citep{snoek2012practical})

\end{itemize}

\section{Report and Submission}

For your write-up, follow the report template at
\url{https://github.com/cs287/hw_template}. Be sure to include a link
to your code, Kaggle ID, and reports on your results.

In addition to submitting your Kaggle results, we also expect you to report on your 
experimental process. This should include data tables, graphs and discussion of any 
issues that you may run into. 

\bibliographystyle{apalike} 
\bibliography{HW1}

\end{document}
